---
title: 'O\*Net Demands and Resources: Associations with Stress, Burnout, and Engagement'
author:
  - name: Renata Garcia Prieto Palacios Roji
    affil: 1
    orcid: '0000-0002-1099-3857'
  - name: Alicia Stachowski
    affil: 2
  - name: John Kulas
    affil: 1
affiliation:
  - num: 1
    address: Montclair State University
  - num: 2
    address: University of Wisonsin-Stout
primary_colour: "#640d14"      ## https://coolors.co/250902-38040e-640d14-800e13-ad2831
secondary_colour: "#ad2831"
accent_colour: "#38040e"
column_numbers: 3
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144/2020/10/presidential-seal.svg
logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144//2020/10/hawk-logo-color.svg
csl: "apa7.csl"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Introduction

Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker & Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which in turn have an impact on job performance. We further extend these perspectives to include challenge and hindrance demands. This study explores how these work experiences empirically relate to engagement, stress, and burnout. Prior to presenting the current study in detail, we provide a brief overview of the relevant theoretical and empirical work on these topics.

## Objectives



# Methods



# Results

We used `posterdown` version `r packageVersion("posterdown")` [@R-posterdown].

```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

 Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Next Steps



# Conclusion

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
