---
title: 'O\*Net Demands and Resources: Associations with Stress, Burnout, and Engagement'
author:
  - name: Renata Garcia Prieto Palacios Roji
    affil: 1
    orcid: '0000-0002-1099-3857'
  - name: Alicia Stachowski
    affil: 2
  - name: John Kulas
    affil: 1
affiliation:
  - num: 1
    address: Montclair State University
  - num: 2
    address: University of Wisonsin-Stout
primary_colour: "#640d14"      ## https://coolors.co/250902-38040e-640d14-800e13-ad2831
secondary_colour: "#ad2831"
accent_colour: "#38040e"
column_numbers: 3
#logoright_name: https&#58;//www.uwstout.edu/sites/default/files/styles/medium/public/2020-12/stoutlogo_quill.jpg?h=93e672f9&itok=68FWq9LN

#logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144/2020/10/presidential-seal.svg
#logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144//2020/10/hawk-logo-color.svg
csl: "apa7.csl"
output: 
  posterdown::posterdown_betterland:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction
Research on the job demands-resources theory (Bakker & Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which in turn have an impact on job performance. We extend these perspectives to include challenge and hindrance demands. This study explores how these work experiences empirically relate to different work outcomes. 

We propose that job elements appraised as “challenge demands” would activate a positive state (i.e., engagement). In contrast, elements of ones job appraised as a hindrance demand would activate a negative state (i.e., stress). Additionally, we sought to explore whether or not the appraisal of a demand as a challenge or hindrance would be related differently to engagement, stress, and burnout.

> *Hypothesis 1:* Job characteristics appraised as resources will be positively associated with engagement, and negatively associated with stress and burnout.

> *Hypothesis 2:* Job characteristics appraised as challenge demands will be positively associated with engagement, and negatively associated with stress and burnout.

> *Hypothesis 3:* Job characteristics appraised as hindrance demands will be negatively associated with engagement, and positively associated with stress and burnout.

# Methods
We evaluated associations between the antecedents and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), within the unifying framework of ONet. Specifically, focusing on the relationship between job components and employee levels of job engagement, job stress, and burnout.

Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020). We further categorized these into “knowledge” (n = 320) versus “skill” (n = 214) occupations. 

### Participants 
Our sample consists of 568 Prolific Panel participants, out of which 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years. Ages ranged from 18-65 with an avergae of 28.18 years old (SD = 7.53). 

### Materials

**Characteristics, Demands, and Resources.** O*Net’s classifications of work activity (including Information Input,  Interacting with Others, Mental Processes, and Work Output) and work context (including Interpersonal Relationships, Physical Work Conditions, and Structural Job Characteristics) were used.

**Burnout and Stress.** The Copenhagen Psychosocial Questionnaire was used (Burr et al., 2019), including 4 burnout and 3 stress items with current sample α’s of 0.85 (burnout) and 0.85 (stress). 

**Engagement.** The 18-item engagement measure specifies three subscales which yielded current sample α’s of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication; Russell et al., 2022). For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91). 

### Procedure
Data was collected through Prolific, a data collection platform. Participants are emailed regarding their eligibility to participate and voluntarily respond to the survey. The requirements to participate included being 18 or older and holding a part- or full-time job. 

# Results

#### Resources
The average perception that an O*Net job element could be considered a resource was 3.77 with a standard deviation of 0.48 (see Table1). Regression analyses reveal that the more a work characteristic is perceived as a resource, the more engaged is the respondent (R2 = .15, F(7, 528) = 12.82, p < .001). There was a only a trivial effect between being viewed as a resource and stress (R2 = .03, F(7, 528) = 2.20, p = .032) and no significant association between being viewed as a resource and burnout (R2 = .01, F(7, 528) = 1.12, p = .348). 

#### Challenges
Across all items, the average perception that an O*Net job element could be considered a challenge was 3.75 with a standard deviation of 0.50 (see Table 2). Regressions reveal that the impact of challenging demands on engagement was similar in direction and magnitude to that of resources, as consistent with JD-R predictions (R2 = .13, F(7, 528) = 11.03, p < .001), with null effects for both stress (R2 = .01, F(7, 528) = 0.88, p = .520) and burnout (R2 = .02, F(7, 528) = 1.21, p = .295). That is, workplace challenges were predictive of engagement but not self-reported stress or burnout, partially supporting H2. 

#### Hinderances
Across all items, the average perception that an O*Net job element could be considered a hindrance was 2.39 with a standard deviation of 0.7 (see Table 3). There was a marginal association between a work characteristic being perceived as a greater hindrance and lower levels of engagement (R2 = .07, F(7, 528) = 5.84, p < .001), with similar effects both between being viewed as a hindrance and increased stress (R2 = .06, F(7, 528) = 4.88, p < .001) as well as increased levels of burnout (R2 = .06, F(7, 528) = 4.90, p < .001), also providing partial support for H3. 

We used `posterdown` version `r packageVersion("posterdown")` [@R-posterdown].

```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

 Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}

```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}


```

# Next Steps



# Conclusion

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
