---
title: 'O\*Net Demands and Resources: Associations with Stress, Burnout, and Engagement'
author:
  - name: Renata Garcia Prieto Palacios Roji
    affil: 1
    orcid: '0000-0002-1099-3857'
  - name: Alicia Stachowski
    affil: 2
  - name: John Kulas
    affil: 1
affiliation:
  - num: 1
    address: Montclair State University
  - num: 2
    address: University of Wisonsin-Stout
primary_colour: "#640d14"      ## https://coolors.co/250902-38040e-640d14-800e13-ad2831
secondary_colour: "#ad2831"
accent_colour: "#38040e"
column_numbers: 3
#logoright_name: https&#58;//www.uwstout.edu/sites/default/files/styles/medium/public/2020-12/stoutlogo_quill.jpg?h=93e672f9&itok=68FWq9LN

#logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144/2020/10/presidential-seal.svg
#logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144//2020/10/hawk-logo-color.svg
csl: "apa7.csl"
output: 
  posterdown::posterdown_betterland:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Introduction
Research on the later job demands-resources theory (Bakker & Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which in turn have an impact on job performance. We extend these perspectives to include challenge and hindrance demands. This study explores how these work experiences empirically relate to engagement, stress, and burnout. 

## Job Demands-Resources Theory
Accordingn to JDR, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: health impairment (resulting from demands) or motivation (resulting from resources; Bakker & Demerouti, 2014). Although some research on job demands in particular is based on a priori classifications of demands (Searle & Auton, 2015), the classification of any work characteristic as a demand or resource is largely subjective. 

+ *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+ *Demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al., 2001).

## The Challenge-Hinderance Framework

Cavanaugh et al. (2000) identified two forms of demands – that of challenge and hindrance demands. This particular distinction has been valuable in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000). 

+ *Challenge demands* promote mastery, personal growth, and future gains. 
+ *Hindrance demands* inhibit growth, learning and goal achievement. 

## Objectives
Drawing on the JDR theory and the challenge-hindrance framework, we propose that job elements appraised as “challenge demands” would activate a positive state – that of engagement. In contrast, elements of ones job appraised as a hindrance demand would activate a negative state (i.e., stress).
We sought to explore whether or not the appraisal of a demand as a challenge or hindrance would be related differently to three organizational outcomes: engagement, workplace stress and burnout.

*Hypothesis 1:* Job characteristics appraised as resources will be positively associated with engagement, and negatively associated with stress and burnout.
*Hypothesis 2:* Job characteristics appraised as challenge demands will be positively associated with engagement, and negatively associated with stress and burnout.
*Hypothesis 3:* Job characteristics appraised as hindrance demands will be negatively associated with engagement, and positively associated with stress and burnout.

# Methods
We evaluate associations between the antecedents and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of ONet. Specifically, we focus on the relationship between ONet delineated job components and employee levels of job engagement, job stress, and burnout with a U.S. workforce representative sample.

## Participants 



# Results

We used `posterdown` version `r packageVersion("posterdown")` [@R-posterdown].

```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

 Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}

```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}


```

# Next Steps



# Conclusion

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
