---
title: 'The Experience of O*Net Work Experiences as Demands and Resources'
author:
  - name: Renata Garcia Prieto Palacios Roji
    affil: 1
    orcid: '0000-0002-1099-3857'
  - name:  Dr. Alicia Stachowski
    affil: 2
  - name: Dr. John Kulas
    affil: 1
affiliation:
  - num: 1
    address: Montclair State University
  - num: 2
    address: University of Wisonsin-Stout
primary_colour: "#640d14"      ## https://coolors.co/250902-38040e-640d14-800e13-ad2831
secondary_colour: "#FDFEFF"
accent_colour: "#38040e"
column_numbers: 3
body_textsize: "50px"
logoright_name: 'Quill_White.png'
logoleft_name: https&#58;//www.montclair.edu/university-communications/wp-content/uploads/sites/144//2020/10/hawk-logo-color.svg
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo=FALSE}

/*                         https://www.w3schools.com/css/css3_images.asp                  */

.logo_left {
  position: absolute;
  top: 0px;
  left: 0px;
  width: 550px;         
  height: 540px;
}


.logo_right {
  position: absolute;
  top: 0px;
  left: 3250px;
  width: 1000px;          
  height: 540px;
}

```

# Introduction

The major objective of this project is to document whether job characteristics (from O*NET) should be interpreted as possibly vacillating between resources and demands (Bakker & Demerouti, 2017). We further present descriptive information regarding which job characteristics are deemed the strongest as well as most variable resources and demands across jobs and by type of employee (knowledge or skill worker classification).

* Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
* Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
* Hypothesis 3a-c: Some of the variability in evaluation as (a) resources, (b) challenge demands, and (c) hindrance demands may be attributable to the type of work being done. 

# Methods  

### Participants & Procedure  

* 568 respondents, 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
* Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
* Gender: female (52.58%) or male (46.83%). 
* Job classifications: International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020), and further categorized into “knowledge” (n = 320) versus “skilled” (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.

The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job. Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.

### Materials

We used 98 statements taken directly from O*NET’s “activity” and “context” classifications. 
Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high). Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) …this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) …this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) …this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

# Results

H1: Resources and challenges are agreed upon (range of lowest 10 resource SDs is 0.70-0.88; challenge 0.79-0.87). Hindrances varied more: SDs 1.32-1.41, providing support for H1. 

H2: There is some overlap between the highest rated resource and job challenge categories (7 of 10 of the highest rated resources and challenge demands across workers were shared)We do not see such a pattern regarding hindrance stressors, generally suggesting support for H2. 

H3: There is overlap between those reported by knowledge and skilled workers. Of the top 10, 8 of the challenge demands, 9 of the hindrance demands, and 7 of the resources overlapped by both knowledge and skilled workers. Independent-samples t-tests revealed the top 3 resources and challenge demands were rated higher by skilled workers, whereas the top 2 hindrance demands were rated higher by knowledge workers. In sum, these results suggest partial support for H3a-c. 


```{r study1, warning=FALSE}

temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

x <- paste("item", sep="",1:404)
y <- t(temp[2,])
                                        ## decluttering Qualtrics excess
data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
colnames(data) <- x

incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]                                          

data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))

colnames(data3) <- x

rm(x, y, temp)       

use <- rbind(data,data3)

## STILL NEED FILE WITH BAD RESPONDENTS IDENTIFIED (E.G., Item_18=2, na > 200, longstring > 20, CARELESS CHECKS > 1)

library(careless)
use$careless_long <- longstring(use[18:399])
use$missing <- rowSums(is.na(use[18:404])) 

different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]

attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]

data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
data <- data[,c(1:404)]

numtot <- nrow(use)
numkicked <- nrow(different)
numvalid <- nrow(data)

```

```{r demos, warning=FALSE}

a <- descr::freq(use$item401, plot=FALSE)

use$item402[use$item402 == "Female " | use$item402 == "female" | use$item402 == "FEMALE" | use$item402 == "Woman" | use$item402 == "Mujer" | use$item402 == "feminine" | use$item402 == "fEMALE" | use$item402 == "F" | use$item402 == "Femenale" | use$item402 == "feminino" | use$item402 == "female " | use$item402 == "Fem" | use$item402 == "Feminine" | use$item402 == "feminine" | use$item402 == "WOMAN" | use$item402 == "Femal" | use$item402 == "femenine" | use$item402 == "Femenine" | use$item402 == "femenino" | use$item402 == "woman"]  <- "Female"

use$item402[use$item402 == "gerente" | use$item402 == "M" | use$item402 == "Make" | use$item402 == "Mal" | use$item402 == "male" | use$item402 == "MALE" | use$item402 == "male" | use$item402 == "Male" | use$item402 == "mals" | use$item402 == "man" | use$item402 == "masculine" | use$item402 == "Masculine" | use$item402 == "Man" | use$item402 == "mals " | use$item402 == "male " | use$item402 == "Male "]  <- "Male"

b <- descr::freq(use$item402, plot=FALSE)

##Job title
library(labourR)


#ESCO/ISCO classification using the labourR package
#ISCO = International Standard Classification of Occupations

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()

ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1) 

m3 <-merge(attention, ISCO, by.x = "id", by.y = "id", all.x = TRUE)

c <- descr::freq(m3$preferredLabel, plot=FALSE)

knowledge <- data[ which(m3$iscoGroup == "1" | m3$iscoGroup == "2"), ]
service <- data[ which(m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"), ]

data$item403[data$item403 == 2000]  <- 20

```


```{r generalrecodes}
## Qualtrics data all messed up

data$item82[data$item82 == 8]  <- 1
data$item82[data$item82 == 9]  <- 2
data$item82[data$item82 == 10] <- 3
data$item82[data$item82 == 11] <- 4
data$item82[data$item82 == 12] <- 5

data$item118[data$item118 == 9]  <- 1
data$item118[data$item118 == 10] <- 2
data$item118[data$item118 == 11] <- 3
data$item118[data$item118 == 12] <- 4
data$item118[data$item118 == 13] <- 5

data$item119[data$item119 == 11] <- 1
data$item119[data$item119 == 12] <- 2
data$item119[data$item119 == 13] <- 3
data$item119[data$item119 == 14] <- 4
data$item119[data$item119 == 15] <- 5

data$item120[data$item120 == 6]  <- 1
data$item120[data$item120 == 7]  <- 2
data$item120[data$item120 == 8]  <- 3
data$item120[data$item120 == 9]  <- 4
data$item120[data$item120 == 10] <- 5

data$item121[data$item121 == 6]  <- 1
data$item121[data$item121 == 7]  <- 2
data$item121[data$item121 == 8]  <- 3
data$item121[data$item121 == 9]  <- 4
data$item121[data$item121 == 10] <- 5

data$item122[data$item122 == 6]  <- 1
data$item122[data$item122 == 7]  <- 2
data$item122[data$item122 == 8]  <- 3
data$item122[data$item122 == 9]  <- 4
data$item122[data$item122 == 10] <- 5

data$item123[data$item123 == 6]  <- 1
data$item123[data$item123 == 7]  <- 2
data$item123[data$item123 == 8]  <- 3
data$item123[data$item123 == 9]  <- 4
data$item123[data$item123 == 10] <- 5

data$item124[data$item124 == 6]  <- 1
data$item124[data$item124 == 7]  <- 2
data$item124[data$item124 == 8]  <- 3
data$item124[data$item124 == 9]  <- 4
data$item124[data$item124 == 10] <- 5

data$item125[data$item125 == 6]  <- 1
data$item125[data$item125 == 7]  <- 2
data$item125[data$item125 == 8]  <- 3
data$item125[data$item125 == 9]  <- 4
data$item125[data$item125 == 10] <- 5

data$item126[data$item126 == 11]  <- 1
data$item126[data$item126 == 12]  <- 2
data$item126[data$item126 == 13]  <- 3
data$item126[data$item126 == 14]  <- 4
data$item126[data$item126 == 15]  <- 5

data$item127[data$item127 == 4]  <- 1
data$item127[data$item127 == 5]  <- 2
data$item127[data$item127 == 6]  <- 3
data$item127[data$item127 == 7]  <- 4
data$item127[data$item127 == 8]  <- 5

data$item128[data$item128 == 11]  <- 1
data$item128[data$item128 == 12]  <- 2
data$item128[data$item128 == 13]  <- 3
data$item128[data$item128 == 14]  <- 4
data$item128[data$item128 == 15]  <- 5

data$item129[data$item129 == 11]  <- 1
data$item129[data$item129 == 12]  <- 2
data$item129[data$item129 == 13]  <- 3
data$item129[data$item129 == 14]  <- 4
data$item129[data$item129 == 15]  <- 5

data$item130[data$item130 == 11]  <- 1
data$item130[data$item130 == 12]  <- 2
data$item130[data$item130 == 13]  <- 3
data$item130[data$item130 == 14]  <- 4
data$item130[data$item130 == 15]  <- 5

data$item131[data$item131 == 11]  <- 1
data$item131[data$item131 == 12]  <- 2
data$item131[data$item131 == 13]  <- 3
data$item131[data$item131 == 14]  <- 4
data$item131[data$item131 == 15]  <- 5

data$item132[data$item132 == 11]  <- 1
data$item132[data$item132 == 12]  <- 2
data$item132[data$item132 == 13]  <- 3
data$item132[data$item132 == 14]  <- 4
data$item132[data$item132 == 15]  <- 5

data$item133[data$item133 == 11]  <- 1
data$item133[data$item133 == 12]  <- 2
data$item133[data$item133 == 13]  <- 3
data$item133[data$item133 == 14]  <- 4
data$item133[data$item133 == 15]  <- 5

data$item134[data$item134 == 11]  <- 1
data$item134[data$item134 == 12]  <- 2
data$item134[data$item134 == 13]  <- 3
data$item134[data$item134 == 14]  <- 4
data$item134[data$item134 == 15]  <- 5

data$item135[data$item135 == 6]  <- 1
data$item135[data$item135 == 7]  <- 2
data$item135[data$item135 == 8]  <- 3
data$item135[data$item135 == 9]  <- 4
data$item135[data$item135 == 10] <- 5

data$item136[data$item136 == 6]  <- 1
data$item136[data$item136 == 7]  <- 2
data$item136[data$item136 == 8]  <- 3
data$item136[data$item136 == 9]  <- 4
data$item136[data$item136 == 10] <- 5

data$item137[data$item137 == 6]  <- 1
data$item137[data$item137 == 7]  <- 2
data$item137[data$item137 == 8]  <- 3
data$item137[data$item137 == 9]  <- 4
data$item137[data$item137 == 10] <- 5

data$item138[data$item138 == 16]  <- 1
data$item138[data$item138 == 17]  <- 2
data$item138[data$item138 == 18]  <- 3
data$item138[data$item138 == 19]  <- 4
data$item138[data$item138 == 20]  <- 5

data$item139[data$item139 == 6]  <- 1
data$item139[data$item139 == 7]  <- 2
data$item139[data$item139 == 8]  <- 3
data$item139[data$item139 == 9]  <- 4
data$item139[data$item139 == 10] <- 5

data$item140[data$item140 == 6]  <- 1
data$item140[data$item140 == 7]  <- 2
data$item140[data$item140 == 8]  <- 3
data$item140[data$item140 == 9]  <- 4
data$item140[data$item140 == 10] <- 5

data$item141[data$item141 == 6]  <- 1
data$item141[data$item141 == 7]  <- 2
data$item141[data$item141 == 8]  <- 3
data$item141[data$item141 == 9]  <- 4
data$item141[data$item141 == 10] <- 5

data$item142[data$item142 == 6]  <- 1
data$item142[data$item142 == 7]  <- 2
data$item142[data$item142 == 8]  <- 3
data$item142[data$item142 == 9]  <- 4
data$item142[data$item142 == 10] <- 5

data$item143[data$item143 == 6]  <- 1
data$item143[data$item143 == 7]  <- 2
data$item143[data$item143 == 8]  <- 3
data$item143[data$item143 == 9]  <- 4
data$item143[data$item143 == 10] <- 5

data$item144[data$item144 == 6]  <- 1
data$item144[data$item144 == 7]  <- 2
data$item144[data$item144 == 8]  <- 3
data$item144[data$item144 == 9]  <- 4
data$item144[data$item144 == 10] <- 5

## Attention check = 145

data$item146[data$item146 == 16]  <- 1
data$item146[data$item146 == 17]  <- 2
data$item146[data$item146 == 18]  <- 3
data$item146[data$item146 == 19]  <- 4
data$item146[data$item146 == 20]  <- 5

data$item147[data$item147 == 6]  <- 1
data$item147[data$item147 == 7]  <- 2
data$item147[data$item147 == 8]  <- 3
data$item147[data$item147 == 9]  <- 4
data$item147[data$item147 == 10] <- 5

data$item148[data$item148 == 6]  <- 1
data$item148[data$item148 == 7]  <- 2
data$item148[data$item148 == 8]  <- 3
data$item148[data$item148 == 9]  <- 4
data$item148[data$item148 == 10] <- 5

data$item149[data$item149 == 6]  <- 1
data$item149[data$item149 == 7]  <- 2
data$item149[data$item149 == 8]  <- 3
data$item149[data$item149 == 9]  <- 4
data$item149[data$item149 == 10] <- 5

data$item150[data$item150 == 11]  <- 1
data$item150[data$item150 == 12]  <- 2
data$item150[data$item150 == 13]  <- 3
data$item150[data$item150 == 14]  <- 4
data$item150[data$item150 == 15]  <- 5

data$item151[data$item151 == 11]  <- 1
data$item151[data$item151 == 12]  <- 2
data$item151[data$item151 == 13]  <- 3
data$item151[data$item151 == 14]  <- 4
data$item151[data$item151 == 15]  <- 5

data$item152[data$item152 == 11]  <- 1
data$item152[data$item152 == 12]  <- 2
data$item152[data$item152 == 13]  <- 3
data$item152[data$item152 == 14]  <- 4
data$item152[data$item152 == 15]  <- 5

data$item153[data$item153 == 11]  <- 1
data$item153[data$item153 == 12]  <- 2
data$item153[data$item153 == 13]  <- 3
data$item153[data$item153 == 14]  <- 4
data$item153[data$item153 == 15]  <- 5

data$item154[data$item154 == 11]  <- 1
data$item154[data$item154 == 12]  <- 2
data$item154[data$item154 == 13]  <- 3
data$item154[data$item154 == 14]  <- 4
data$item154[data$item154 == 15]  <- 5

data$item155[data$item155 == 11]  <- 1
data$item155[data$item155 == 12]  <- 2
data$item155[data$item155 == 13]  <- 3
data$item155[data$item155 == 14]  <- 4
data$item155[data$item155 == 15]  <- 5

data$item156[data$item156 == 11]  <- 1
data$item156[data$item156 == 12]  <- 2
data$item156[data$item156 == 13]  <- 3
data$item156[data$item156 == 14]  <- 4
data$item156[data$item156 == 15]  <- 5

data$item157[data$item157 == 11]  <- 1
data$item157[data$item157 == 12]  <- 2
data$item157[data$item157 == 13]  <- 3
data$item157[data$item157 == 14]  <- 4
data$item157[data$item157 == 15]  <- 5

data$item158[data$item158 == 6]  <- 1
data$item158[data$item158 == 7]  <- 2
data$item158[data$item158 == 8]  <- 3
data$item158[data$item158 == 9]  <- 4
data$item158[data$item158 == 10] <- 5

data$item159[data$item159 == 11]  <- 1
data$item159[data$item159 == 12]  <- 2
data$item159[data$item159 == 13]  <- 3
data$item159[data$item159 == 14]  <- 4
data$item159[data$item159 == 15]  <- 5

data$item160[data$item160 == 11]  <- 1
data$item160[data$item160 == 12]  <- 2
data$item160[data$item160 == 13]  <- 3
data$item160[data$item160 == 14]  <- 4
data$item160[data$item160 == 15]  <- 5

data$item161[data$item161 == 6]  <- 1
data$item161[data$item161 == 7]  <- 2
data$item161[data$item161 == 8]  <- 3
data$item161[data$item161 == 9]  <- 4
data$item161[data$item161 == 10] <- 5

data$item162[data$item162 == 11]  <- 1
data$item162[data$item162 == 12]  <- 2
data$item162[data$item162 == 13]  <- 3
data$item162[data$item162 == 14]  <- 4
data$item162[data$item162 == 15]  <- 5

data$item163[data$item163 == 11]  <- 1
data$item163[data$item163 == 12]  <- 2
data$item163[data$item163 == 13]  <- 3
data$item163[data$item163 == 14]  <- 4
data$item163[data$item163 == 15]  <- 5

data$item164[data$item164 == 11]  <- 1
data$item164[data$item164 == 12]  <- 2
data$item164[data$item164 == 13]  <- 3
data$item164[data$item164 == 14]  <- 4
data$item164[data$item164 == 15]  <- 5

data$item165[data$item165 == 11]  <- 1
data$item165[data$item165 == 12]  <- 2
data$item165[data$item165 == 13]  <- 3
data$item165[data$item165 == 14]  <- 4
data$item165[data$item165 == 15]  <- 5

data$item166[data$item166 == 11]  <- 1
data$item166[data$item166 == 12]  <- 2
data$item166[data$item166 == 13]  <- 3
data$item166[data$item166 == 14]  <- 4
data$item166[data$item166 == 15]  <- 5

data$item167[data$item167 == 18]  <- 1
data$item167[data$item167 == 19]  <- 2
data$item167[data$item167 == 20]  <- 3
data$item167[data$item167 == 21]  <- 4
data$item167[data$item167 == 22]  <- 5

data$item168[data$item168 == 11]  <- 1
data$item168[data$item168 == 12]  <- 2
data$item168[data$item168 == 13]  <- 3
data$item168[data$item168 == 14]  <- 4
data$item168[data$item168 == 15]  <- 5

data$item169[data$item169 == 11]  <- 1
data$item169[data$item169 == 12]  <- 2
data$item169[data$item169 == 13]  <- 3
data$item169[data$item169 == 14]  <- 4
data$item169[data$item169 == 15]  <- 5

data$item170[data$item170 == 11]  <- 1
data$item170[data$item170 == 12]  <- 2
data$item170[data$item170 == 13]  <- 3
data$item170[data$item170 == 14]  <- 4
data$item170[data$item170 == 15]  <- 5

data$item171[data$item171 == 11]  <- 1
data$item171[data$item171 == 12]  <- 2
data$item171[data$item171 == 13]  <- 3
data$item171[data$item171 == 14]  <- 4
data$item171[data$item171 == 15]  <- 5

data$item172[data$item172 == 11]  <- 1
data$item172[data$item172 == 12]  <- 2
data$item172[data$item172 == 13]  <- 3
data$item172[data$item172 == 14]  <- 4
data$item172[data$item172 == 15]  <- 5

data$item173[data$item173 == 11]  <- 1
data$item173[data$item173 == 12]  <- 2
data$item173[data$item173 == 13]  <- 3
data$item173[data$item173 == 14]  <- 4
data$item173[data$item173 == 15]  <- 5

data$item174[data$item174 == 11]  <- 1
data$item174[data$item174 == 12]  <- 2
data$item174[data$item174 == 13]  <- 3
data$item174[data$item174 == 14]  <- 4
data$item174[data$item174 == 15]  <- 5

data$item175[data$item175 == 11]  <- 1
data$item175[data$item175 == 12]  <- 2
data$item175[data$item175 == 13]  <- 3
data$item175[data$item175 == 14]  <- 4
data$item175[data$item175 == 15]  <- 5

data$item176[data$item176 == 11]  <- 1
data$item176[data$item176 == 12]  <- 2
data$item176[data$item176 == 13]  <- 3
data$item176[data$item176 == 14]  <- 4
data$item176[data$item176 == 15]  <- 5

data$item177[data$item177 == 11]  <- 1
data$item177[data$item177 == 12]  <- 2
data$item177[data$item177 == 13]  <- 3
data$item177[data$item177 == 14]  <- 4
data$item177[data$item177 == 15]  <- 5

data$item178[data$item178 == 11]  <- 1
data$item178[data$item178 == 12]  <- 2
data$item178[data$item178 == 13]  <- 3
data$item178[data$item178 == 14]  <- 4
data$item178[data$item178 == 15]  <- 5

data$item179[data$item179 == 11]  <- 1
data$item179[data$item179 == 12]  <- 2
data$item179[data$item179 == 13]  <- 3
data$item179[data$item179 == 14]  <- 4
data$item179[data$item179 == 15]  <- 5

data$item180[data$item180 == 11]  <- 1
data$item180[data$item180 == 12]  <- 2
data$item180[data$item180 == 13]  <- 3
data$item180[data$item180 == 14]  <- 4
data$item180[data$item180 == 15]  <- 5

data$item181[data$item181 == 11]  <- 1
data$item181[data$item181 == 12]  <- 2
data$item181[data$item181 == 13]  <- 3
data$item181[data$item181 == 14]  <- 4
data$item181[data$item181 == 15]  <- 5

data$item182[data$item182 == 11]  <- 1
data$item182[data$item182 == 12]  <- 2
data$item182[data$item182 == 13]  <- 3
data$item182[data$item182 == 14]  <- 4
data$item182[data$item182 == 15]  <- 5

data$item183[data$item183 == 11]  <- 1
data$item183[data$item183 == 12]  <- 2
data$item183[data$item183 == 13]  <- 3
data$item183[data$item183 == 14]  <- 4
data$item183[data$item183 == 15]  <- 5

data$item184[data$item184 == 21]  <- 1
data$item184[data$item184 == 22]  <- 2
data$item184[data$item184 == 23]  <- 3
data$item184[data$item184 == 24]  <- 4
data$item184[data$item184 == 25]  <- 5

data$item185[data$item185 == 11]  <- 1
data$item185[data$item185 == 12]  <- 2
data$item185[data$item185 == 13]  <- 3
data$item185[data$item185 == 14]  <- 4
data$item185[data$item185 == 15]  <- 5

data$item186[data$item186 == 11]  <- 1
data$item186[data$item186 == 12]  <- 2
data$item186[data$item186 == 13]  <- 3
data$item186[data$item186 == 14]  <- 4
data$item186[data$item186 == 15]  <- 5

data$item187[data$item187 == 11]  <- 1
data$item187[data$item187 == 12]  <- 2
data$item187[data$item187 == 13]  <- 3
data$item187[data$item187 == 14]  <- 4
data$item187[data$item187 == 15]  <- 5

data$item188[data$item188 == 11]  <- 1
data$item188[data$item188 == 12]  <- 2
data$item188[data$item188 == 13]  <- 3
data$item188[data$item188 == 14]  <- 4
data$item188[data$item188 == 15]  <- 5

data$item189[data$item189 == 11]  <- 1
data$item189[data$item189 == 12]  <- 2
data$item189[data$item189 == 13]  <- 3
data$item189[data$item189 == 14]  <- 4
data$item189[data$item189 == 15]  <- 5

data$item190[data$item190 == 11]  <- 1
data$item190[data$item190 == 12]  <- 2
data$item190[data$item190 == 13]  <- 3
data$item190[data$item190 == 14]  <- 4
data$item190[data$item190 == 15]  <- 5

data$item191[data$item191 == 11]  <- 1
data$item191[data$item191 == 12]  <- 2
data$item191[data$item191 == 13]  <- 3
data$item191[data$item191 == 14]  <- 4
data$item191[data$item191 == 15]  <- 5

data$item192[data$item192 == 11]  <- 1
data$item192[data$item192 == 12]  <- 2
data$item192[data$item192 == 13]  <- 3
data$item192[data$item192 == 14]  <- 4
data$item192[data$item192 == 15]  <- 5

data$item193[data$item193 == 11]  <- 1
data$item193[data$item193 == 12]  <- 2
data$item193[data$item193 == 13]  <- 3
data$item193[data$item193 == 14]  <- 4
data$item193[data$item193 == 15]  <- 5

data$item194[data$item194 == 11]  <- 1
data$item194[data$item194 == 12]  <- 2
data$item194[data$item194 == 13]  <- 3
data$item194[data$item194 == 14]  <- 4
data$item194[data$item194 == 15]  <- 5

data$item195[data$item195 == 11]  <- 1
data$item195[data$item195 == 12]  <- 2
data$item195[data$item195 == 13]  <- 3
data$item195[data$item195 == 14]  <- 4
data$item195[data$item195 == 15]  <- 5

data$item196[data$item196 == 11]  <- 1
data$item196[data$item196 == 12]  <- 2
data$item196[data$item196 == 13]  <- 3
data$item196[data$item196 == 14]  <- 4
data$item196[data$item196 == 15]  <- 5

data$item197[data$item197 == 11]  <- 1
data$item197[data$item197 == 12]  <- 2
data$item197[data$item197 == 13]  <- 3
data$item197[data$item197 == 14]  <- 4
data$item197[data$item197 == 15]  <- 5

data$item198[data$item198 == 11]  <- 1
data$item198[data$item198 == 12]  <- 2
data$item198[data$item198 == 13]  <- 3
data$item198[data$item198 == 14]  <- 4
data$item198[data$item198 == 15]  <- 5

data$item199[data$item199 == 11]  <- 1
data$item199[data$item199 == 12]  <- 2
data$item199[data$item199 == 13]  <- 3
data$item199[data$item199 == 14]  <- 4
data$item199[data$item199 == 15]  <- 5

data$item200[data$item200 == 11]  <- 1
data$item200[data$item200 == 12]  <- 2
data$item200[data$item200 == 13]  <- 3
data$item200[data$item200 == 14]  <- 4
data$item200[data$item200 == 15]  <- 5

data$item201[data$item201 == 11]  <- 1
data$item201[data$item201 == 12]  <- 2
data$item201[data$item201 == 13]  <- 3
data$item201[data$item201 == 14]  <- 4
data$item201[data$item201 == 15]  <- 5

data$item202[data$item202 == 11]  <- 1
data$item202[data$item202 == 12]  <- 2
data$item202[data$item202 == 13]  <- 3
data$item202[data$item202 == 14]  <- 4
data$item202[data$item202 == 15]  <- 5

data$item203[data$item203 == 9]   <- 1
data$item203[data$item203 == 10]  <- 2
data$item203[data$item203 == 11]  <- 3
data$item203[data$item203 == 12]  <- 4
data$item203[data$item203 == 13]  <- 5

data$item204[data$item204 == 11]  <- 1
data$item204[data$item204 == 12]  <- 2
data$item204[data$item204 == 13]  <- 3
data$item204[data$item204 == 14]  <- 4
data$item204[data$item204 == 15]  <- 5

data$item205[data$item205 == 6]  <- 1
data$item205[data$item205 == 7]  <- 2
data$item205[data$item205 == 8]  <- 3
data$item205[data$item205 == 9]  <- 4
data$item205[data$item205 == 10] <- 5

data$item206[data$item206 == 6]  <- 1
data$item206[data$item206 == 7]  <- 2
data$item206[data$item206 == 8]  <- 3
data$item206[data$item206 == 9]  <- 4
data$item206[data$item206 == 10] <- 5

data$item207[data$item207 == 6]  <- 1
data$item207[data$item207 == 7]  <- 2
data$item207[data$item207 == 8]  <- 3
data$item207[data$item207 == 9]  <- 4
data$item207[data$item207 == 10] <- 5

data$item208[data$item208 == 6]  <- 1
data$item208[data$item208 == 7]  <- 2
data$item208[data$item208 == 8]  <- 3
data$item208[data$item208 == 9]  <- 4
data$item208[data$item208 == 10] <- 5

data$item209[data$item209 == 6]  <- 1
data$item209[data$item209 == 7]  <- 2
data$item209[data$item209 == 8]  <- 3
data$item209[data$item209 == 9]  <- 4
data$item209[data$item209 == 10] <- 5

data$item210[data$item210 == 6]  <- 1
data$item210[data$item210 == 7]  <- 2
data$item210[data$item210 == 8]  <- 3
data$item210[data$item210 == 9]  <- 4
data$item210[data$item210 == 10] <- 5

data$item211[data$item211 == 11]  <- 1
data$item211[data$item211 == 12]  <- 2
data$item211[data$item211 == 13]  <- 3
data$item211[data$item211 == 14]  <- 4
data$item211[data$item211 == 15]  <- 5

data$item212[data$item212 == 4]  <- 1
data$item212[data$item212 == 5]  <- 2
data$item212[data$item212 == 6]  <- 3
data$item212[data$item212 == 7]  <- 4
data$item212[data$item212 == 8]  <- 5

data$item213[data$item213 == 11]  <- 1
data$item213[data$item213 == 12]  <- 2
data$item213[data$item213 == 13]  <- 3
data$item213[data$item213 == 14]  <- 4
data$item213[data$item213 == 15]  <- 5

data$item214[data$item214 == 11]  <- 1
data$item214[data$item214 == 12]  <- 2
data$item214[data$item214 == 13]  <- 3
data$item214[data$item214 == 14]  <- 4
data$item214[data$item214 == 15]  <- 5

data$item215[data$item215 == 11]  <- 1
data$item215[data$item215 == 12]  <- 2
data$item215[data$item215 == 13]  <- 3
data$item215[data$item215 == 14]  <- 4
data$item215[data$item215 == 15]  <- 5

data$item216[data$item216 == 11]  <- 1
data$item216[data$item216 == 12]  <- 2
data$item216[data$item216 == 13]  <- 3
data$item216[data$item216 == 14]  <- 4
data$item216[data$item216 == 15]  <- 5

data$item217[data$item217 == 11]  <- 1
data$item217[data$item217 == 12]  <- 2
data$item217[data$item217 == 13]  <- 3
data$item217[data$item217 == 14]  <- 4
data$item217[data$item217 == 15]  <- 5

data$item218[data$item218 == 11]  <- 1
data$item218[data$item218 == 12]  <- 2
data$item218[data$item218 == 13]  <- 3
data$item218[data$item218 == 14]  <- 4
data$item218[data$item218 == 15]  <- 5

data$item219[data$item219 == 11]  <- 1
data$item219[data$item219 == 12]  <- 2
data$item219[data$item219 == 13]  <- 3
data$item219[data$item219 == 14]  <- 4
data$item219[data$item219 == 15]  <- 5

data$item220[data$item220 == 6]  <- 1
data$item220[data$item220 == 7]  <- 2
data$item220[data$item220 == 8]  <- 3
data$item220[data$item220 == 9]  <- 4
data$item220[data$item220 == 10] <- 5

data$item221[data$item221 == 6]  <- 1
data$item221[data$item221 == 7]  <- 2
data$item221[data$item221 == 8]  <- 3
data$item221[data$item221 == 9]  <- 4
data$item221[data$item221 == 10] <- 5

data$item222[data$item222 == 6]  <- 1
data$item222[data$item222 == 7]  <- 2
data$item222[data$item222 == 8]  <- 3
data$item222[data$item222 == 9]  <- 4
data$item222[data$item222 == 10] <- 5

data$item223[data$item223 == 16] <- 1
data$item223[data$item223 == 17] <- 2
data$item223[data$item223 == 18] <- 3
data$item223[data$item223 == 19] <- 4
data$item223[data$item223 == 20] <- 5

data$item224[data$item224 == 6]  <- 1
data$item224[data$item224 == 7]  <- 2
data$item224[data$item224 == 8]  <- 3
data$item224[data$item224 == 9]  <- 4
data$item224[data$item224 == 10] <- 5

data$item225[data$item225 == 6]  <- 1
data$item225[data$item225 == 7]  <- 2
data$item225[data$item225 == 8]  <- 3
data$item225[data$item225 == 9]  <- 4
data$item225[data$item225 == 10] <- 5

data$item226[data$item226 == 6]  <- 1
data$item226[data$item226 == 7]  <- 2
data$item226[data$item226 == 8]  <- 3
data$item226[data$item226 == 9]  <- 4
data$item226[data$item226 == 10] <- 5

data$item227[data$item227 == 6]  <- 1
data$item227[data$item227 == 7]  <- 2
data$item227[data$item227 == 8]  <- 3
data$item227[data$item227 == 9]  <- 4
data$item227[data$item227 == 10] <- 5

data$item228[data$item228 == 6]  <- 1
data$item228[data$item228 == 7]  <- 2
data$item228[data$item228 == 8]  <- 3
data$item228[data$item228 == 9]  <- 4
data$item228[data$item228 == 10] <- 5

data$item229[data$item229 == 6]  <- 1
data$item229[data$item229 == 7]  <- 2
data$item229[data$item229 == 8]  <- 3
data$item229[data$item229 == 9]  <- 4
data$item229[data$item229 == 10] <- 5

data$item230[data$item230 == 16] <- 1
data$item230[data$item230 == 17] <- 2
data$item230[data$item230 == 18] <- 3
data$item230[data$item230 == 19] <- 4
data$item230[data$item230 == 20] <- 5

data$item231[data$item231 == 6]  <- 1
data$item231[data$item231 == 7]  <- 2
data$item231[data$item231 == 8]  <- 3
data$item231[data$item231 == 9]  <- 4
data$item231[data$item231 == 10] <- 5

data$item232[data$item232 == 6]  <- 1
data$item232[data$item232 == 7]  <- 2
data$item232[data$item232 == 8]  <- 3
data$item232[data$item232 == 9]  <- 4
data$item232[data$item232 == 10] <- 5

data$item233[data$item233 == 6]  <- 1
data$item233[data$item233 == 7]  <- 2
data$item233[data$item233 == 8]  <- 3
data$item233[data$item233 == 9]  <- 4
data$item233[data$item233 == 10] <- 5

data$item234[data$item234 == 11]  <- 1
data$item234[data$item234 == 12]  <- 2
data$item234[data$item234 == 13]  <- 3
data$item234[data$item234 == 14]  <- 4
data$item234[data$item234 == 15]  <- 5

data$item235[data$item235 == 11]  <- 1
data$item235[data$item235 == 12]  <- 2
data$item235[data$item235 == 13]  <- 3
data$item235[data$item235 == 14]  <- 4
data$item235[data$item235 == 15]  <- 5

data$item236[data$item236 == 11]  <- 1
data$item236[data$item236 == 12]  <- 2
data$item236[data$item236 == 13]  <- 3
data$item236[data$item236 == 14]  <- 4
data$item236[data$item236 == 15]  <- 5

data$item237[data$item237 == 11]  <- 1
data$item237[data$item237 == 12]  <- 2
data$item237[data$item237 == 13]  <- 3
data$item237[data$item237 == 14]  <- 4
data$item237[data$item237 == 15]  <- 5

data$item238[data$item238 == 11]  <- 1
data$item238[data$item238 == 12]  <- 2
data$item238[data$item238 == 13]  <- 3
data$item238[data$item238 == 14]  <- 4
data$item238[data$item238 == 15]  <- 5

data$item239[data$item239 == 11]  <- 1
data$item239[data$item239 == 12]  <- 2
data$item239[data$item239 == 13]  <- 3
data$item239[data$item239 == 14]  <- 4
data$item239[data$item239 == 15]  <- 5

data$item240[data$item240 == 11]  <- 1
data$item240[data$item240 == 12]  <- 2
data$item240[data$item240 == 13]  <- 3
data$item240[data$item240 == 14]  <- 4
data$item240[data$item240 == 15]  <- 5

data$item241[data$item241 == 11]  <- 1
data$item241[data$item241 == 12]  <- 2
data$item241[data$item241 == 13]  <- 3
data$item241[data$item241 == 14]  <- 4
data$item241[data$item241 == 15]  <- 5

data$item242[data$item242 == 6]  <- 1
data$item242[data$item242 == 7]  <- 2
data$item242[data$item242 == 8]  <- 3
data$item242[data$item242 == 9]  <- 4
data$item242[data$item242 == 10] <- 5

data$item243[data$item243 == 11]  <- 1
data$item243[data$item243 == 12]  <- 2
data$item243[data$item243 == 13]  <- 3
data$item243[data$item243 == 14]  <- 4
data$item243[data$item243 == 15]  <- 5

data$item244[data$item244 == 11]  <- 1
data$item244[data$item244 == 12]  <- 2
data$item244[data$item244 == 13]  <- 3
data$item244[data$item244 == 14]  <- 4
data$item244[data$item244 == 15]  <- 5

data$item245[data$item245 == 6]  <- 1
data$item245[data$item245 == 7]  <- 2
data$item245[data$item245 == 8]  <- 3
data$item245[data$item245 == 9]  <- 4
data$item245[data$item245 == 10] <- 5

data$item246[data$item246 == 11]  <- 1
data$item246[data$item246 == 12]  <- 2
data$item246[data$item246 == 13]  <- 3
data$item246[data$item246 == 14]  <- 4
data$item246[data$item246 == 15]  <- 5

data$item247[data$item247 == 11]  <- 1
data$item247[data$item247 == 12]  <- 2
data$item247[data$item247 == 13]  <- 3
data$item247[data$item247 == 14]  <- 4
data$item247[data$item247 == 15]  <- 5

## Attention check

data$item249[data$item249 == 11]  <- 1
data$item249[data$item249 == 12]  <- 2
data$item249[data$item249 == 13]  <- 3
data$item249[data$item249 == 14]  <- 4
data$item249[data$item249 == 15]  <- 5

data$item250[data$item250 == 11]  <- 1
data$item250[data$item250 == 12]  <- 2
data$item250[data$item250 == 13]  <- 3
data$item250[data$item250 == 14]  <- 4
data$item250[data$item250 == 15]  <- 5

data$item251[data$item251 == 11]  <- 1
data$item251[data$item251 == 12]  <- 2
data$item251[data$item251 == 13]  <- 3
data$item251[data$item251 == 14]  <- 4
data$item251[data$item251 == 15]  <- 5

data$item252[data$item252 == 18]  <- 1
data$item252[data$item252 == 19]  <- 2
data$item252[data$item252 == 20]  <- 3
data$item252[data$item252 == 21]  <- 4
data$item252[data$item252 == 22]  <- 5

data$item253[data$item253 == 11]  <- 1
data$item253[data$item253 == 12]  <- 2
data$item253[data$item253 == 13]  <- 3
data$item253[data$item253 == 14]  <- 4
data$item253[data$item253 == 15]  <- 5

data$item254[data$item254 == 11]  <- 1
data$item254[data$item254 == 12]  <- 2
data$item254[data$item254 == 13]  <- 3
data$item254[data$item254 == 14]  <- 4
data$item254[data$item254 == 15]  <- 5

data$item255[data$item255 == 11]  <- 1
data$item255[data$item255 == 12]  <- 2
data$item255[data$item255 == 13]  <- 3
data$item255[data$item255 == 14]  <- 4
data$item255[data$item255 == 15]  <- 5

data$item256[data$item256 == 11]  <- 1
data$item256[data$item256 == 12]  <- 2
data$item256[data$item256 == 13]  <- 3
data$item256[data$item256 == 14]  <- 4
data$item256[data$item256 == 15]  <- 5

data$item257[data$item257 == 11]  <- 1
data$item257[data$item257 == 12]  <- 2
data$item257[data$item257 == 13]  <- 3
data$item257[data$item257 == 14]  <- 4
data$item257[data$item257 == 15]  <- 5

data$item258[data$item258 == 11]  <- 1
data$item258[data$item258 == 12]  <- 2
data$item258[data$item258 == 13]  <- 3
data$item258[data$item258 == 14]  <- 4
data$item258[data$item258 == 15]  <- 5

data$item259[data$item259 == 11]  <- 1
data$item259[data$item259 == 12]  <- 2
data$item259[data$item259 == 13]  <- 3
data$item259[data$item259 == 14]  <- 4
data$item259[data$item259 == 15]  <- 5

data$item260[data$item260 == 11]  <- 1
data$item260[data$item260 == 12]  <- 2
data$item260[data$item260 == 13]  <- 3
data$item260[data$item260 == 14]  <- 4
data$item260[data$item260 == 15]  <- 5

data$item261[data$item261 == 11]  <- 1
data$item261[data$item261 == 12]  <- 2
data$item261[data$item261 == 13]  <- 3
data$item261[data$item261 == 14]  <- 4
data$item261[data$item261 == 15]  <- 5

data$item262[data$item262 == 11]  <- 1
data$item262[data$item262 == 12]  <- 2
data$item262[data$item262 == 13]  <- 3
data$item262[data$item262 == 14]  <- 4
data$item262[data$item262 == 15]  <- 5

data$item263[data$item263 == 11]  <- 1
data$item263[data$item263 == 12]  <- 2
data$item263[data$item263 == 13]  <- 3
data$item263[data$item263 == 14]  <- 4
data$item263[data$item263 == 15]  <- 5

data$item264[data$item264 == 11]  <- 1
data$item264[data$item264 == 12]  <- 2
data$item264[data$item264 == 13]  <- 3
data$item264[data$item264 == 14]  <- 4
data$item264[data$item264 == 15]  <- 5

data$item265[data$item265 == 11]  <- 1
data$item265[data$item265 == 12]  <- 2
data$item265[data$item265 == 13]  <- 3
data$item265[data$item265 == 14]  <- 4
data$item265[data$item265 == 15]  <- 5

data$item266[data$item266 == 11]  <- 1
data$item266[data$item266 == 12]  <- 2
data$item266[data$item266 == 13]  <- 3
data$item266[data$item266 == 14]  <- 4
data$item266[data$item266 == 15]  <- 5

data$item267[data$item267 == 11]  <- 1
data$item267[data$item267 == 12]  <- 2
data$item267[data$item267 == 13]  <- 3
data$item267[data$item267 == 14]  <- 4
data$item267[data$item267 == 15]  <- 5

data$item268[data$item268 == 11]  <- 1
data$item268[data$item268 == 12]  <- 2
data$item268[data$item268 == 13]  <- 3
data$item268[data$item268 == 14]  <- 4
data$item268[data$item268 == 15]  <- 5

data$item269[data$item269 == 21]  <- 1
data$item269[data$item269 == 22]  <- 2
data$item269[data$item269 == 23]  <- 3
data$item269[data$item269 == 24]  <- 4
data$item269[data$item269 == 25]  <- 5

data$item270[data$item270 == 11]  <- 1
data$item270[data$item270 == 12]  <- 2
data$item270[data$item270 == 13]  <- 3
data$item270[data$item270 == 14]  <- 4
data$item270[data$item270 == 15]  <- 5

data$item271[data$item271 == 11]  <- 1
data$item271[data$item271 == 12]  <- 2
data$item271[data$item271 == 13]  <- 3
data$item271[data$item271 == 14]  <- 4
data$item271[data$item271 == 15]  <- 5

data$item272[data$item272 == 11]  <- 1
data$item272[data$item272 == 12]  <- 2
data$item272[data$item272 == 13]  <- 3
data$item272[data$item272 == 14]  <- 4
data$item272[data$item272 == 15]  <- 5

data$item273[data$item273 == 11]  <- 1
data$item273[data$item273 == 12]  <- 2
data$item273[data$item273 == 13]  <- 3
data$item273[data$item273 == 14]  <- 4
data$item273[data$item273 == 15]  <- 5

data$item274[data$item274 == 11]  <- 1
data$item274[data$item274 == 12]  <- 2
data$item274[data$item274 == 13]  <- 3
data$item274[data$item274 == 14]  <- 4
data$item274[data$item274 == 15]  <- 5

data$item275[data$item275 == 11]  <- 1
data$item275[data$item275 == 12]  <- 2
data$item275[data$item275 == 13]  <- 3
data$item275[data$item275 == 14]  <- 4
data$item275[data$item275 == 15]  <- 5

data$item276[data$item276 == 11]  <- 1
data$item276[data$item276 == 12]  <- 2
data$item276[data$item276 == 13]  <- 3
data$item276[data$item276 == 14]  <- 4
data$item276[data$item276 == 15]  <- 5

data$item277[data$item277 == 11]  <- 1
data$item277[data$item277 == 12]  <- 2
data$item277[data$item277 == 13]  <- 3
data$item277[data$item277 == 14]  <- 4
data$item277[data$item277 == 15]  <- 5

data$item278[data$item278 == 11]  <- 1
data$item278[data$item278 == 12]  <- 2
data$item278[data$item278 == 13]  <- 3
data$item278[data$item278 == 14]  <- 4
data$item278[data$item278 == 15]  <- 5

data$item279[data$item279 == 11]  <- 1
data$item279[data$item279 == 12]  <- 2
data$item279[data$item279 == 13]  <- 3
data$item279[data$item279 == 14]  <- 4
data$item279[data$item279 == 15]  <- 5

data$item280[data$item280 == 11]  <- 1
data$item280[data$item280 == 12]  <- 2
data$item280[data$item280 == 13]  <- 3
data$item280[data$item280 == 14]  <- 4
data$item280[data$item280 == 15]  <- 5

data$item281[data$item281 == 11]  <- 1
data$item281[data$item281 == 12]  <- 2
data$item281[data$item281 == 13]  <- 3
data$item281[data$item281 == 14]  <- 4
data$item281[data$item281 == 15]  <- 5

data$item282[data$item282 == 11]  <- 1
data$item282[data$item282 == 12]  <- 2
data$item282[data$item282 == 13]  <- 3
data$item282[data$item282 == 14]  <- 4
data$item282[data$item282 == 15]  <- 5

data$item283[data$item283 == 11]  <- 1
data$item283[data$item283 == 12]  <- 2
data$item283[data$item283 == 13]  <- 3
data$item283[data$item283 == 14]  <- 4
data$item283[data$item283 == 15]  <- 5

data$item284[data$item284 == 11]  <- 1
data$item284[data$item284 == 12]  <- 2
data$item284[data$item284 == 13]  <- 3
data$item284[data$item284 == 14]  <- 4
data$item284[data$item284 == 15]  <- 5

data$item285[data$item285 == 11]  <- 1
data$item285[data$item285 == 12]  <- 2
data$item285[data$item285 == 13]  <- 3
data$item285[data$item285 == 14]  <- 4
data$item285[data$item285 == 15]  <- 5

data$item286[data$item286 == 11]  <- 1
data$item286[data$item286 == 12]  <- 2
data$item286[data$item286 == 13]  <- 3
data$item286[data$item286 == 14]  <- 4
data$item286[data$item286 == 15]  <- 5

data$item287[data$item287 == 11]  <- 1
data$item287[data$item287 == 12]  <- 2
data$item287[data$item287 == 13]  <- 3
data$item287[data$item287 == 14]  <- 4
data$item287[data$item287 == 15]  <- 5

data$item288[data$item288 == 9]   <- 1
data$item288[data$item288 == 10]  <- 2
data$item288[data$item288 == 11]  <- 3
data$item288[data$item288 == 12]  <- 4
data$item288[data$item288 == 13]  <- 5

data$item289[data$item289 == 11]  <- 1
data$item289[data$item289 == 12]  <- 2
data$item289[data$item289 == 13]  <- 3
data$item289[data$item289 == 14]  <- 4
data$item289[data$item289 == 15]  <- 5

data$item290[data$item290 == 6]  <- 1
data$item290[data$item290 == 7]  <- 2
data$item290[data$item290 == 8]  <- 3
data$item290[data$item290 == 9]  <- 4
data$item290[data$item290 == 10] <- 5

data$item291[data$item291 == 6]  <- 1
data$item291[data$item291 == 7]  <- 2
data$item291[data$item291 == 8]  <- 3
data$item291[data$item291 == 9]  <- 4
data$item291[data$item291 == 10] <- 5

data$item292[data$item292 == 6]  <- 1
data$item292[data$item292 == 7]  <- 2
data$item292[data$item292 == 8]  <- 3
data$item292[data$item292 == 9]  <- 4
data$item292[data$item292 == 10] <- 5

data$item293[data$item293 == 6]  <- 1
data$item293[data$item293 == 7]  <- 2
data$item293[data$item293 == 8]  <- 3
data$item293[data$item293 == 9]  <- 4
data$item293[data$item293 == 10] <- 5

data$item294[data$item294 == 6]  <- 1
data$item294[data$item294 == 7]  <- 2
data$item294[data$item294 == 8]  <- 3
data$item294[data$item294 == 9]  <- 4
data$item294[data$item294 == 10] <- 5

data$item295[data$item295 == 6]  <- 1
data$item295[data$item295 == 7]  <- 2
data$item295[data$item295 == 8]  <- 3
data$item295[data$item295 == 9]  <- 4
data$item295[data$item295 == 10] <- 5

data$item296[data$item296 == 11]  <- 1
data$item296[data$item296 == 12]  <- 2
data$item296[data$item296 == 13]  <- 3
data$item296[data$item296 == 14]  <- 4
data$item296[data$item296 == 15]  <- 5

data$item297[data$item297 == 4]  <- 1
data$item297[data$item297 == 5]  <- 2
data$item297[data$item297 == 6]  <- 3
data$item297[data$item297 == 7]  <- 4
data$item297[data$item297 == 8]  <- 5

data$item298[data$item298 == 11]  <- 1
data$item298[data$item298 == 12]  <- 2
data$item298[data$item298 == 13]  <- 3
data$item298[data$item298 == 14]  <- 4
data$item298[data$item298 == 15]  <- 5

data$item299[data$item299 == 11]  <- 1
data$item299[data$item299 == 12]  <- 2
data$item299[data$item299 == 13]  <- 3
data$item299[data$item299 == 14]  <- 4
data$item299[data$item299 == 15]  <- 5

data$item300[data$item300 == 11]  <- 1
data$item300[data$item300 == 12]  <- 2
data$item300[data$item300 == 13]  <- 3
data$item300[data$item300 == 14]  <- 4
data$item300[data$item300 == 15]  <- 5

data$item301[data$item301 == 11]  <- 1
data$item301[data$item301 == 12]  <- 2
data$item301[data$item301 == 13]  <- 3
data$item301[data$item301 == 14]  <- 4
data$item301[data$item301 == 15]  <- 5

data$item302[data$item302 == 11]  <- 1
data$item302[data$item302 == 12]  <- 2
data$item302[data$item302 == 13]  <- 3
data$item302[data$item302 == 14]  <- 4
data$item302[data$item302 == 15]  <- 5

data$item303[data$item303 == 11]  <- 1
data$item303[data$item303 == 12]  <- 2
data$item303[data$item303 == 13]  <- 3
data$item303[data$item303 == 14]  <- 4
data$item303[data$item303 == 15]  <- 5

data$item304[data$item304 == 11]  <- 1
data$item304[data$item304 == 12]  <- 2
data$item304[data$item304 == 13]  <- 3
data$item304[data$item304 == 14]  <- 4
data$item304[data$item304 == 15]  <- 5

data$item305[data$item305 == 6]  <- 1
data$item305[data$item305 == 7]  <- 2
data$item305[data$item305 == 8]  <- 3
data$item305[data$item305 == 9]  <- 4
data$item305[data$item305 == 10] <- 5

data$item306[data$item306 == 6]  <- 1
data$item306[data$item306 == 7]  <- 2
data$item306[data$item306 == 8]  <- 3
data$item306[data$item306 == 9]  <- 4
data$item306[data$item306 == 10] <- 5

data$item307[data$item307 == 6]  <- 1
data$item307[data$item307 == 7]  <- 2
data$item307[data$item307 == 8]  <- 3
data$item307[data$item307 == 9]  <- 4
data$item307[data$item307 == 10] <- 5

## Attention check

data$item309[data$item309 == 16]  <- 1
data$item309[data$item309 == 17]  <- 2
data$item309[data$item309 == 18]  <- 3
data$item309[data$item309 == 19]  <- 4
data$item309[data$item309 == 20]  <- 5

data$item310[data$item310 == 6]  <- 1
data$item310[data$item310 == 7]  <- 2
data$item310[data$item310 == 8]  <- 3
data$item310[data$item310 == 9]  <- 4
data$item310[data$item310 == 10] <- 5

data$item311[data$item311 == 6]  <- 1
data$item311[data$item311 == 7]  <- 2
data$item311[data$item311 == 8]  <- 3
data$item311[data$item311 == 9]  <- 4
data$item311[data$item311 == 10] <- 5

data$item312[data$item312 == 6]  <- 1
data$item312[data$item312 == 7]  <- 2
data$item312[data$item312 == 8]  <- 3
data$item312[data$item312 == 9]  <- 4
data$item312[data$item312 == 10] <- 5

data$item313[data$item313 == 6]  <- 1
data$item313[data$item313 == 7]  <- 2
data$item313[data$item313 == 8]  <- 3
data$item313[data$item313 == 9]  <- 4
data$item313[data$item313 == 10] <- 5

data$item314[data$item314 == 6]  <- 1
data$item314[data$item314 == 7]  <- 2
data$item314[data$item314 == 8]  <- 3
data$item314[data$item314 == 9]  <- 4
data$item314[data$item314 == 10] <- 5

data$item315[data$item315 == 6]  <- 1
data$item315[data$item315 == 7]  <- 2
data$item315[data$item315 == 8]  <- 3
data$item315[data$item315 == 9]  <- 4
data$item315[data$item315 == 10] <- 5

data$item316[data$item316 == 16]  <- 1
data$item316[data$item316 == 17]  <- 2
data$item316[data$item316 == 18]  <- 3
data$item316[data$item316 == 19]  <- 4
data$item316[data$item316 == 20]  <- 5

data$item317[data$item317 == 6]  <- 1
data$item317[data$item317 == 7]  <- 2
data$item317[data$item317 == 8]  <- 3
data$item317[data$item317 == 9]  <- 4
data$item317[data$item317 == 10] <- 5

data$item318[data$item318 == 6]  <- 1
data$item318[data$item318 == 7]  <- 2
data$item318[data$item318 == 8]  <- 3
data$item318[data$item318 == 9]  <- 4
data$item318[data$item318 == 10] <- 5

data$item319[data$item319 == 6]  <- 1
data$item319[data$item319 == 7]  <- 2
data$item319[data$item319 == 8]  <- 3
data$item319[data$item319 == 9]  <- 4
data$item319[data$item319 == 10] <- 5

data$item320[data$item320 == 11] <- 1
data$item320[data$item320 == 12] <- 2
data$item320[data$item320 == 13] <- 3
data$item320[data$item320 == 14] <- 4
data$item320[data$item320 == 15] <- 5

data$item321[data$item321 == 11] <- 1
data$item321[data$item321 == 12] <- 2
data$item321[data$item321 == 13] <- 3
data$item321[data$item321 == 14] <- 4
data$item321[data$item321 == 15] <- 5

data$item322[data$item322 == 11] <- 1
data$item322[data$item322 == 12] <- 2
data$item322[data$item322 == 13] <- 3
data$item322[data$item322 == 14] <- 4
data$item322[data$item322 == 15] <- 5

data$item323[data$item323 == 11] <- 1
data$item323[data$item323 == 12] <- 2
data$item323[data$item323 == 13] <- 3
data$item323[data$item323 == 14] <- 4
data$item323[data$item323 == 15] <- 5

data$item324[data$item324 == 11] <- 1
data$item324[data$item324 == 12] <- 2
data$item324[data$item324 == 13] <- 3
data$item324[data$item324 == 14] <- 4
data$item324[data$item324 == 15] <- 5

data$item325[data$item325 == 11] <- 1
data$item325[data$item325 == 12] <- 2
data$item325[data$item325 == 13] <- 3
data$item325[data$item325 == 14] <- 4
data$item325[data$item325 == 15] <- 5

data$item326[data$item326 == 11] <- 1
data$item326[data$item326 == 12] <- 2
data$item326[data$item326 == 13] <- 3
data$item326[data$item326 == 14] <- 4
data$item326[data$item326 == 15] <- 5

data$item327[data$item327 == 11] <- 1
data$item327[data$item327 == 12] <- 2
data$item327[data$item327 == 13] <- 3
data$item327[data$item327 == 14] <- 4
data$item327[data$item327 == 15] <- 5

data$item328[data$item328 == 6]  <- 1
data$item328[data$item328 == 7]  <- 2
data$item328[data$item328 == 8]  <- 3
data$item328[data$item328 == 9]  <- 4
data$item328[data$item328 == 10] <- 5

data$item329[data$item329 == 11] <- 1
data$item329[data$item329 == 12] <- 2
data$item329[data$item329 == 13] <- 3
data$item329[data$item329 == 14] <- 4
data$item329[data$item329 == 15] <- 5

data$item330[data$item330 == 11] <- 1
data$item330[data$item330 == 12] <- 2
data$item330[data$item330 == 13] <- 3
data$item330[data$item330 == 14] <- 4
data$item330[data$item330 == 15] <- 5

data$item331[data$item331 == 6]  <- 1
data$item331[data$item331 == 7]  <- 2
data$item331[data$item331 == 8]  <- 3
data$item331[data$item331 == 9]  <- 4
data$item331[data$item331 == 10] <- 5

data$item332[data$item332 == 11] <- 1
data$item332[data$item332 == 12] <- 2
data$item332[data$item332 == 13] <- 3
data$item332[data$item332 == 14] <- 4
data$item332[data$item332 == 15] <- 5

data$item333[data$item333 == 11] <- 1
data$item333[data$item333 == 12] <- 2
data$item333[data$item333 == 13] <- 3
data$item333[data$item333 == 14] <- 4
data$item333[data$item333 == 15] <- 5

data$item334[data$item334 == 11] <- 1
data$item334[data$item334 == 12] <- 2
data$item334[data$item334 == 13] <- 3
data$item334[data$item334 == 14] <- 4
data$item334[data$item334 == 15] <- 5

data$item335[data$item335 == 11] <- 1
data$item335[data$item335 == 12] <- 2
data$item335[data$item335 == 13] <- 3
data$item335[data$item335 == 14] <- 4
data$item335[data$item335 == 15] <- 5

data$item336[data$item336 == 11] <- 1
data$item336[data$item336 == 12] <- 2
data$item336[data$item336 == 13] <- 3
data$item336[data$item336 == 14] <- 4
data$item336[data$item336 == 15] <- 5

data$item337[data$item337 == 18] <- 1
data$item337[data$item337 == 19] <- 2
data$item337[data$item337 == 20] <- 3
data$item337[data$item337 == 21] <- 4
data$item337[data$item337 == 22] <- 5

data$item338[data$item338 == 11] <- 1
data$item338[data$item338 == 12] <- 2
data$item338[data$item338 == 13] <- 3
data$item338[data$item338 == 14] <- 4
data$item338[data$item338 == 15] <- 5

data$item339[data$item339 == 11] <- 1
data$item339[data$item339 == 12] <- 2
data$item339[data$item339 == 13] <- 3
data$item339[data$item339 == 14] <- 4
data$item339[data$item339 == 15] <- 5

data$item340[data$item340 == 11] <- 1
data$item340[data$item340 == 12] <- 2
data$item340[data$item340 == 13] <- 3
data$item340[data$item340 == 14] <- 4
data$item340[data$item340 == 15] <- 5

data$item341[data$item341 == 11] <- 1
data$item341[data$item341 == 12] <- 2
data$item341[data$item341 == 13] <- 3
data$item341[data$item341 == 14] <- 4
data$item341[data$item341 == 15] <- 5

data$item342[data$item342 == 11] <- 1
data$item342[data$item342 == 12] <- 2
data$item342[data$item342 == 13] <- 3
data$item342[data$item342 == 14] <- 4
data$item342[data$item342 == 15] <- 5

data$item343[data$item343 == 11] <- 1
data$item343[data$item343 == 12] <- 2
data$item343[data$item343 == 13] <- 3
data$item343[data$item343 == 14] <- 4
data$item343[data$item343 == 15] <- 5

data$item344[data$item344 == 11] <- 1
data$item344[data$item344 == 12] <- 2
data$item344[data$item344 == 13] <- 3
data$item344[data$item344 == 14] <- 4
data$item344[data$item344 == 15] <- 5

data$item345[data$item345 == 11] <- 1
data$item345[data$item345 == 12] <- 2
data$item345[data$item345 == 13] <- 3
data$item345[data$item345 == 14] <- 4
data$item345[data$item345 == 15] <- 5

data$item346[data$item346 == 11] <- 1
data$item346[data$item346 == 12] <- 2
data$item346[data$item346 == 13] <- 3
data$item346[data$item346 == 14] <- 4
data$item346[data$item346 == 15] <- 5

data$item347[data$item347 == 11] <- 1
data$item347[data$item347 == 12] <- 2
data$item347[data$item347 == 13] <- 3
data$item347[data$item347 == 14] <- 4
data$item347[data$item347 == 15] <- 5

data$item348[data$item348 == 11] <- 1
data$item348[data$item348 == 12] <- 2
data$item348[data$item348 == 13] <- 3
data$item348[data$item348 == 14] <- 4
data$item348[data$item348 == 15] <- 5

data$item349[data$item349 == 11] <- 1
data$item349[data$item349 == 12] <- 2
data$item349[data$item349 == 13] <- 3
data$item349[data$item349 == 14] <- 4
data$item349[data$item349 == 15] <- 5

data$item350[data$item350 == 11] <- 1
data$item350[data$item350 == 12] <- 2
data$item350[data$item350 == 13] <- 3
data$item350[data$item350 == 14] <- 4
data$item350[data$item350 == 15] <- 5

data$item351[data$item351 == 11] <- 1
data$item351[data$item351 == 12] <- 2
data$item351[data$item351 == 13] <- 3
data$item351[data$item351 == 14] <- 4
data$item351[data$item351 == 15] <- 5

data$item352[data$item352 == 11] <- 1
data$item352[data$item352 == 12] <- 2
data$item352[data$item352 == 13] <- 3
data$item352[data$item352 == 14] <- 4
data$item352[data$item352 == 15] <- 5

data$item353[data$item353 == 11] <- 1
data$item353[data$item353 == 12] <- 2
data$item353[data$item353 == 13] <- 3
data$item353[data$item353 == 14] <- 4
data$item353[data$item353 == 15] <- 5

data$item354[data$item354 == 21] <- 1
data$item354[data$item354 == 22] <- 2
data$item354[data$item354 == 23] <- 3
data$item354[data$item354 == 24] <- 4
data$item354[data$item354 == 25] <- 5

data$item355[data$item355 == 11] <- 1
data$item355[data$item355 == 12] <- 2
data$item355[data$item355 == 13] <- 3
data$item355[data$item355 == 14] <- 4
data$item355[data$item355 == 15] <- 5

data$item356[data$item356 == 11] <- 1
data$item356[data$item356 == 12] <- 2
data$item356[data$item356 == 13] <- 3
data$item356[data$item356 == 14] <- 4
data$item356[data$item356 == 15] <- 5

data$item357[data$item357 == 11] <- 1
data$item357[data$item357 == 12] <- 2
data$item357[data$item357 == 13] <- 3
data$item357[data$item357 == 14] <- 4
data$item357[data$item357 == 15] <- 5

data$item358[data$item358 == 11] <- 1
data$item358[data$item358 == 12] <- 2
data$item358[data$item358 == 13] <- 3
data$item358[data$item358 == 14] <- 4
data$item358[data$item358 == 15] <- 5

data$item359[data$item359 == 11] <- 1
data$item359[data$item359 == 12] <- 2
data$item359[data$item359 == 13] <- 3
data$item359[data$item359 == 14] <- 4
data$item359[data$item359 == 15] <- 5

data$item360[data$item360 == 11] <- 1
data$item360[data$item360 == 12] <- 2
data$item360[data$item360 == 13] <- 3
data$item360[data$item360 == 14] <- 4
data$item360[data$item360 == 15] <- 5

data$item361[data$item361 == 11] <- 1
data$item361[data$item361 == 12] <- 2
data$item361[data$item361 == 13] <- 3
data$item361[data$item361 == 14] <- 4
data$item361[data$item361 == 15] <- 5

data$item362[data$item362 == 11] <- 1
data$item362[data$item362 == 12] <- 2
data$item362[data$item362 == 13] <- 3
data$item362[data$item362 == 14] <- 4
data$item362[data$item362 == 15] <- 5

data$item363[data$item363 == 11] <- 1
data$item363[data$item363 == 12] <- 2
data$item363[data$item363 == 13] <- 3
data$item363[data$item363 == 14] <- 4
data$item363[data$item363 == 15] <- 5

data$item364[data$item364 == 11] <- 1
data$item364[data$item364 == 12] <- 2
data$item364[data$item364 == 13] <- 3
data$item364[data$item364 == 14] <- 4
data$item364[data$item364 == 15] <- 5

data$item365[data$item365 == 11] <- 1
data$item365[data$item365 == 12] <- 2
data$item365[data$item365 == 13] <- 3
data$item365[data$item365 == 14] <- 4
data$item365[data$item365 == 15] <- 5

data$item366[data$item366 == 11] <- 1
data$item366[data$item366 == 12] <- 2
data$item366[data$item366 == 13] <- 3
data$item366[data$item366 == 14] <- 4
data$item366[data$item366 == 15] <- 5

data$item367[data$item367 == 11] <- 1
data$item367[data$item367 == 12] <- 2
data$item367[data$item367 == 13] <- 3
data$item367[data$item367 == 14] <- 4
data$item367[data$item367 == 15] <- 5

data$item368[data$item368 == 11] <- 1
data$item368[data$item368 == 12] <- 2
data$item368[data$item368 == 13] <- 3
data$item368[data$item368 == 14] <- 4
data$item368[data$item368 == 15] <- 5

data$item369[data$item369 == 11] <- 1
data$item369[data$item369 == 12] <- 2
data$item369[data$item369 == 13] <- 3
data$item369[data$item369 == 14] <- 4
data$item369[data$item369 == 15] <- 5

data$item370[data$item370 == 11] <- 1
data$item370[data$item370 == 12] <- 2
data$item370[data$item370 == 13] <- 3
data$item370[data$item370 == 14] <- 4
data$item370[data$item370 == 15] <- 5

data$item371[data$item371 == 11] <- 1
data$item371[data$item371 == 12] <- 2
data$item371[data$item371 == 13] <- 3
data$item371[data$item371 == 14] <- 4
data$item371[data$item371 == 15] <- 5

data$item372[data$item372 == 11] <- 1
data$item372[data$item372 == 12] <- 2
data$item372[data$item372 == 13] <- 3
data$item372[data$item372 == 14] <- 4
data$item372[data$item372 == 15] <- 5


```

```{r generalrankings, warning=FALSE, eval=FALSE}
labels <- read.csv("truncatedlabels.csv")            
chars <- as.data.frame(t(data[22:117]))           
chars$description <- labels[c(22:117),1]
chars$mean <- round(rowMeans(chars[1:nrow(data)], na.rm=TRUE),2)
chars$sd   <- round(apply(chars[1:nrow(data)], 1, sd, na.rm=TRUE),2)
chars <- chars[ which(chars$sd > 0), ]        
chars <- chars[,-61]   ## attention check
sortchars <- chars[order(-chars$mean),]
topchars <- head(sortchars, 10)
bottomchars <- tail(sortchars,10)
topchars <- topchars[tail(names(topchars),3)]        
bottomchars <- bottomchars[tail(names(bottomchars),3)]  
library(ggplot2)
overall.chars.t <- ggplot(topchars, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5)) 
overall.chars.b <- ggplot(bottomchars, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
#### Service
chars <- as.data.frame(t(service[22:117]))           
chars$description <- labels[c(22:117),1]
chars$mean <- round(rowMeans(chars[1:nrow(service)], na.rm=TRUE),2)
chars$sd   <- round(apply(chars[1:nrow(service)], 1, sd, na.rm=TRUE),2)
chars <- chars[ which(chars$sd > 0), ]        
chars <- chars[,-61]   ## attention check
sortchars <- chars[order(-chars$mean),]
topchars <- head(sortchars, 10)
bottomchars <- tail(sortchars,10)
topchars <- topchars[tail(names(topchars),3)]        
bottomchars <- bottomchars[tail(names(bottomchars),3)]  
service.t <- ggplot(topchars, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
service.b <- ggplot(bottomchars, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
## Knowledge
chars <- as.data.frame(t(knowledge[22:117]))           
chars$description <- labels[c(22:117),1]
chars$mean <- round(rowMeans(chars[1:nrow(knowledge)], na.rm=TRUE),2)
chars$sd   <- round(apply(chars[1:nrow(knowledge)], 1, sd, na.rm=TRUE),2)
chars <- chars[ which(chars$sd > 0), ]        
chars <- chars[,-61]   ## attention check
sortchars <- chars[order(-chars$mean),]
topchars <- head(sortchars, 10)
bottomchars <- tail(sortchars,10)
topchars <- topchars[tail(names(topchars),3)]        
bottomchars <- bottomchars[tail(names(bottomchars),3)]  
knowledge.t <- ggplot(topchars, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
knowledge.b <- ggplot(bottomchars, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
```

```{r resources, fig.align = "center"}
labels <- read.csv("truncatedlabels.csv")            
resource <- as.data.frame(t(data[118:202]))           
resource$description <- labels[c(118:202),1]
resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
resource <- resource[ which(resource$sd > 0), ]        
resource <- resource[,-145]   ## attention check
sortresource <- resource[order(-resource$mean),]
topresource <- head(sortresource, 10)
bottomresource <- tail(sortresource,10)
topresource <- topresource[tail(names(topresource),3)]        
bottomresource <- bottomresource[tail(names(bottomresource),3)]  
library(ggplot2)
resource.overall.t <- ggplot(topresource, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6)) 

resource.overall.b <- ggplot(bottomresource, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
#### Service
resource <- as.data.frame(t(service[118:202]))           
resource$description <- labels[c(118:202),1]
resource$mean <- round(rowMeans(resource[1:nrow(service)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(service)], 1, sd, na.rm=TRUE),2)
resource <- resource[ which(resource$sd > 0), ]        
resource <- resource[,-145]   ## attention check
sortresource <- resource[order(-resource$mean),]
topresource <- head(sortresource, 10)
bottomresource <- tail(sortresource,10)
topresource <- topresource[tail(names(topresource),3)]        
bottomresource <- bottomresource[tail(names(bottomresource),3)]  
resource.service.t <- ggplot(topresource, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
resource.service.b <- ggplot(bottomresource, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
## Knowledge
resource <- as.data.frame(t(knowledge[118:202]))           
resource$description <- labels[c(118:202),1]
resource$mean <- round(rowMeans(resource[1:nrow(knowledge)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(knowledge)], 1, sd, na.rm=TRUE),2)
resource <- resource[ which(resource$sd > 0), ]        
resource <- resource[,-145]   ## attention check
sortresource <- resource[order(-resource$mean),]
topresource <- head(sortresource, 10)
bottomresource <- tail(sortresource,10)
topresource <- topresource[tail(names(topresource),3)]        
bottomresource <- bottomresource[tail(names(bottomresource),3)]  
resource.knowledge.t <- ggplot(topresource, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
resource.knowledge.b <- ggplot(bottomresource, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
```

```{r figure1, fig.width=14, fig.height=6, fig.cap="Overall Top 10 Resources"}
resource.overall.t
```

```{r challenges}
labels <- read.csv("truncatedlabels.csv")            
challenge <- as.data.frame(t(data[288:372]))           
challenge$description <- labels[c(288:372),1]
challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
challenge <- challenge[ which(challenge$sd > 0), ]        
challenge <- challenge[,-308]   ## attention check
sortchallenge <- challenge[order(-challenge$mean),]
topchallenge <- head(sortchallenge, 10)
bottomchallenge <- tail(sortchallenge,10)
topchallenge <- topchallenge[tail(names(topchallenge),3)]        
bottomchallenge <- bottomchallenge[tail(names(bottomchallenge),3)]  
library(ggplot2)
challenge.overall.t <- ggplot(topchallenge, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="orange", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6)) 
challenge.overall.b <- ggplot(bottomchallenge, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="orange", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
#### Service
challenge <- as.data.frame(t(service[288:372]))           
challenge$description <- labels[c(288:372),1]
challenge$mean <- round(rowMeans(challenge[1:nrow(service)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(service)], 1, sd, na.rm=TRUE),2)
challenge <- challenge[ which(challenge$sd > 0), ]        
challenge <- challenge[,-308]   ## attention check
sortchallenge <- challenge[order(-challenge$mean),]
topchallenge <- head(sortchallenge, 10)
bottomchallenge <- tail(sortchallenge,10)
topchallenge <- topchallenge[tail(names(topchallenge),3)]        
bottomchallenge <- bottomchallenge[tail(names(bottomchallenge),3)]  
challenge.service.t <- ggplot(topchallenge, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="orange", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
challenge.service.b <- ggplot(bottomchallenge, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="orange", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
## Knowledge
challenge <- as.data.frame(t(knowledge[288:372]))           
challenge$description <- labels[c(288:372),1]
challenge$mean <- round(rowMeans(challenge[1:nrow(knowledge)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(knowledge)], 1, sd, na.rm=TRUE),2)
challenge <- challenge[ which(challenge$sd > 0), ]        
challenge <- challenge[,-308]   ## attention check
sortchallenge <- challenge[order(-challenge$mean),]
topchallenge <- head(sortchallenge, 10)
bottomchallenge <- tail(sortchallenge,10)
topchallenge <- topchallenge[tail(names(topchallenge),3)]        
bottomchallenge <- bottomchallenge[tail(names(bottomchallenge),3)]  
challenge.knowledge.t <- ggplot(topchallenge, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="orange", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
challenge.knowledge.b <- ggplot(bottomchallenge, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="orange", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
```

```{r figure2, fig.width=14, fig.height=6, fig.cap="Overall Top 10 Challenge Demands"}
challenge.overall.t
```


```{r hindrances}
labels <- read.csv("truncatedlabels.csv")            
hindrance <- as.data.frame(t(data[203:287]))           
hindrance$description <- labels[c(203:287),1]
hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
hindrance <- hindrance[ which(hindrance$sd > 0), ]        
hindrance <- hindrance[,-248]   ## attention check
sorthindrance <- hindrance[order(-hindrance$mean),]
tophindrance <- head(sorthindrance, 10)
bottomhindrance <- tail(sorthindrance,10)
tophindrance <- tophindrance[tail(names(tophindrance),3)]        
bottomhindrance <- bottomhindrance[tail(names(bottomhindrance),3)]  
library(ggplot2)
hindrance.overall.t <- ggplot(tophindrance, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5)) 
hindrance.overall.b <- ggplot(bottomhindrance, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Overall") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
#### Service
hindrance <- as.data.frame(t(service[203:287]))           
hindrance$description <- labels[c(203:287),1]
hindrance$mean <- round(rowMeans(hindrance[1:nrow(service)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(service)], 1, sd, na.rm=TRUE),2)
hindrance <- hindrance[ which(hindrance$sd > 0), ]        
hindrance <- hindrance[,-248]   ## attention check
sorthindrance <- hindrance[order(-hindrance$mean),]
tophindrance <- head(sorthindrance, 10)
bottomhindrance <- tail(sorthindrance,10)
tophindrance <- tophindrance[tail(names(tophindrance),3)]        
bottomhindrance <- bottomhindrance[tail(names(bottomhindrance),3)]  
hindrance.service.t <- ggplot(tophindrance, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5)) 
hindrance.service.b <- ggplot(bottomhindrance, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Skill") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
## Knowledge
hindrance <- as.data.frame(t(knowledge[203:287]))           
hindrance$description <- labels[c(203:287),1]
hindrance$mean <- round(rowMeans(hindrance[1:nrow(knowledge)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(knowledge)], 1, sd, na.rm=TRUE),2)
hindrance <- hindrance[ which(hindrance$sd > 0), ]        
hindrance <- hindrance[,-248]   ## attention check
sorthindrance <- hindrance[order(-hindrance$mean),]
tophindrance <- head(sorthindrance, 10)
bottomhindrance <- tail(sorthindrance,10)
tophindrance <- tophindrance[tail(names(tophindrance),3)]        
bottomhindrance <- bottomhindrance[tail(names(bottomhindrance),3)]  
hindrance.knowledge.t <- ggplot(tophindrance, aes(x=reorder(description,mean), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
hindrance.knowledge.b <- ggplot(bottomhindrance, aes(x=reorder(description,-mean), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Knowledge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5)) 
```

```{r figure3, fig.width=14, fig.height=6, fig.cap="Overall Top 10 Hindrance Demands"}
hindrance.overall.t
```

```{r resources_variability, eval=TRUE}
labels <- read.csv("truncatedlabels.csv")            
resource <- as.data.frame(t(data[118:202]))           
resource$description <- labels[c(118:202),1]
resource$overallmean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
resource <- resource[,-145]   ## attention check
sortresource <- resource[order(-resource$sd),]
topresource <- head(sortresource, 10)
topresource <- topresource[tail(names(topresource),3)]        
 
data$worker[m3$iscoGroup == "1" | m3$iscoGroup == "2"] <- "Knowledge"
data$worker[m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"] <- "Skill"
t1 <- t.test(item152~worker,data)
t2 <- t.test(item146~worker,data)
t3 <- t.test(item133~worker,data)
t4 <- t.test(item124~worker,data)
t5 <- t.test(item125~worker,data)
t6 <- t.test(item122~worker,data)
t7 <- t.test(item136~worker,data)
t8 <- t.test(item132~worker,data)
t9 <- t.test(item161~worker,data)
t10 <- t.test(item141~worker,data)
t <- rbind(t1$statistic,t2$statistic,t3$statistic,t4$statistic,t5$statistic,t6$statistic,t7$statistic,t8$statistic,t9$statistic,t10$statistic)
p <- rbind(t1$p.value,t2$p.value,t3$p.value,t4$p.value,t5$p.value,t6$p.value,t7$p.value,t8$p.value,t9$p.value,t10$p.value)
Knowledge <- rbind(t1$estimate[[1]],t2$estimate[[1]],t3$estimate[[1]],t4$estimate[[1]],t5$estimate[[1]],t6$estimate[[1]],t7$estimate[[1]],t8$estimate[[1]],t9$estimate[[1]],t10$estimate[[1]])
Skill <- rbind(t1$estimate[[2]],t2$estimate[[2]],t3$estimate[[2]],t4$estimate[[2]],t5$estimate[[2]],t6$estimate[[2]],t7$estimate[[2]],t8$estimate[[2]],t9$estimate[[2]],t10$estimate[[2]])
write.csv(topresource, "topresource.csv")
topresource <- read.csv("topresource.csv")[2:4]
topresourceplot <- cbind(topresource,t,p,Knowledge,Skill)
topresourceplot$p <- round(topresourceplot$p,3)
topresourceplot$Knowledge <- round(topresourceplot$Knowledge,2)
topresourceplot$Skill <- round(topresourceplot$Skill,2)
topresourceplot <- topresourceplot[order(-abs(topresourceplot$t)),]

```

```{r hindrances_variability, eval=FALSE}
labels <- read.csv("truncatedlabels.csv")            
hindrance <- as.data.frame(t(data[203:287]))           
hindrance$description <- labels[c(203:287),1]
hindrance$overallmean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
hindrance <- hindrance[,-248]   ## attention check
sorthindrance <- hindrance[order(-hindrance$sd),]
tophindrance <- head(sorthindrance, 10)
tophindrance <- tophindrance[tail(names(tophindrance),3)]        
 
data$worker[m3$iscoGroup == "1" | m3$iscoGroup == "2"] <- "Knowledge"
data$worker[m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"] <- "Skill"
t1 <- t.test(item206~worker,data)
t2 <- t.test(item203~worker,data)
t3 <- t.test(item284~worker,data)
t4 <- t.test(item230~worker,data)
t5 <- t.test(item239~worker,data)
t6 <- t.test(item281~worker,data)
t7 <- t.test(item267~worker,data)
t8 <- t.test(item218~worker,data)
t9 <- t.test(item236~worker,data)
t10 <- t.test(item261~worker,data)
t <- rbind(t1$statistic,t2$statistic,t3$statistic,t4$statistic,t5$statistic,t6$statistic,t7$statistic,t8$statistic,t9$statistic,t10$statistic)
p <- rbind(t1$p.value,t2$p.value,t3$p.value,t4$p.value,t5$p.value,t6$p.value,t7$p.value,t8$p.value,t9$p.value,t10$p.value)
Knowledge <- rbind(t1$estimate[[1]],t2$estimate[[1]],t3$estimate[[1]],t4$estimate[[1]],t5$estimate[[1]],t6$estimate[[1]],t7$estimate[[1]],t8$estimate[[1]],t9$estimate[[1]],t10$estimate[[1]])
Skill <- rbind(t1$estimate[[2]],t2$estimate[[2]],t3$estimate[[2]],t4$estimate[[2]],t5$estimate[[2]],t6$estimate[[2]],t7$estimate[[2]],t8$estimate[[2]],t9$estimate[[2]],t10$estimate[[2]])
write.csv(tophindrance, "tophindrance.csv")
tophindrance <- read.csv("tophindrance.csv")[2:4]
tophindranceplot <- cbind(tophindrance,t,p,Knowledge,Skill)
tophindranceplot$p <- round(tophindranceplot$p,3)
tophindranceplot$Knowledge <- round(tophindranceplot$Knowledge,2)
tophindranceplot$Skill <- round(tophindranceplot$Skill,2)
tophindranceplot <- tophindranceplot[order(-abs(tophindranceplot$t)),]

```

```{r challenges_variability, eval=FALSE}
labels <- read.csv("truncatedlabels.csv")            
challenge <- as.data.frame(t(data[288:372]))           
challenge$description <- labels[c(288:372),1]
challenge$overallmean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
challenge <- challenge[,-308]   ## attention check
sortchallenge <- challenge[order(-challenge$sd),]
topchallenge <- head(sortchallenge, 10)
topchallenge <- topchallenge[tail(names(topchallenge),3)]        
 
data$worker[m3$iscoGroup == "1" | m3$iscoGroup == "2"] <- "Knowledge"
data$worker[m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"] <- "Skill"
t1 <- t.test(item306~worker,data)
t2 <- t.test(item298~worker,data)
t3 <- t.test(item316~worker,data)
t4 <- t.test(item318~worker,data)
t5 <- t.test(item311~worker,data)
t6 <- t.test(item310~worker,data)
t7 <- t.test(item352~worker,data)
t8 <- t.test(item317~worker,data)
t9 <- t.test(item322~worker,data)
t10 <- t.test(item294~worker,data)
t <- rbind(t1$statistic,t2$statistic,t3$statistic,t4$statistic,t5$statistic,t6$statistic,t7$statistic,t8$statistic,t9$statistic,t10$statistic)
p <- rbind(t1$p.value,t2$p.value,t3$p.value,t4$p.value,t5$p.value,t6$p.value,t7$p.value,t8$p.value,t9$p.value,t10$p.value)
Knowledge <- rbind(t1$estimate[[1]],t2$estimate[[1]],t3$estimate[[1]],t4$estimate[[1]],t5$estimate[[1]],t6$estimate[[1]],t7$estimate[[1]],t8$estimate[[1]],t9$estimate[[1]],t10$estimate[[1]])
Skill <- rbind(t1$estimate[[2]],t2$estimate[[2]],t3$estimate[[2]],t4$estimate[[2]],t5$estimate[[2]],t6$estimate[[2]],t7$estimate[[2]],t8$estimate[[2]],t9$estimate[[2]],t10$estimate[[2]])
write.csv(topchallenge, "topchallenge.csv")
topchallenge <- read.csv("topchallenge.csv")[2:4]
topchallengeplot <- cbind(topchallenge,t,p,Knowledge,Skill)
topchallengeplot$p <- round(topchallengeplot$p,3)
topchallengeplot$Knowledge <- round(topchallengeplot$Knowledge,2)
topchallengeplot$Skill <- round(topchallengeplot$Skill,2)
topchallengeplot <- topchallengeplot[order(-abs(topchallengeplot$t)),]

```

```{r resourceslowsd, eval=FALSE}
labels <- read.csv("truncatedlabels.csv")            
resource <- as.data.frame(t(data[118:202]))           
resource$description <- labels[c(118:202),1]
resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
resource <- resource[,-145]   ## attention check
resource <- resource[ which(resource$sd > 0), ] 
sortresource <- resource[order(resource$sd),]
topresource <- head(sortresource, 10)
topresource <- topresource[tail(names(topresource),3)]        
library(ggplot2)
ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Resources (Agreement)") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5)) 
```

```{r challengesagree, eval=FALSE}
labels <- read.csv("truncatedlabels.csv")            
challenge <- as.data.frame(t(data[288:372]))           
challenge$description <- labels[c(288:372),1]
challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
challenge <- challenge[,-308]   ## attention check
challenge <- challenge[ which(challenge$sd > 0), ] 
sortchallenge <- challenge[order(challenge$sd),]
topchallenge <- head(sortchallenge, 10)
topchallenge <- topchallenge[tail(names(topchallenge),3)]        
library(ggplot2)
ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Agreement (Challenges)") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5)) 
```

```{r hindrancesagree, eval=FALSE}
labels <- read.csv("truncatedlabels.csv")            
hindrance <- as.data.frame(t(data[203:287]))           
hindrance$description <- labels[c(203:287),1]
hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
hindrance <- hindrance[,-248]   ## attention check
hindrance <- hindrance[ which(hindrance$sd > 0), ] 
sorthindrance <- hindrance[order(hindrance$sd),]
tophindrance <- head(sorthindrance, 10)
tophindrance <- tophindrance[tail(names(tophindrance),3)]        
library(ggplot2)
ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="black", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Agreement (Hindrances)") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
```


# Discussion

The findings generally suggest there is greater consensus/less variability regarding ratings of job characteristics deemed resources and challenge demands, but much greater variability in those characteristics rated as hindrances. There was considerable overlap in the top 10 resources that emerged from those classified as knowledge and skill workers. 

These findings provide support for moving away from the a priori classification of job characteristics as either demands or resources. Moreover, demands should be further deliniated as challenges or hindrances. This suggests that overcoming or managing challenge demands may serve the same purpose as a resource, such as increasing motivation and engagement with their work. The overlap between the classification of resources suggests that there might be job characteristics that universally serve as resources to varying degrees depending on the type of work. 

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```
